Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-03-29 src-latex/parts/30-dataset.tex
Minor changes while re-reading

\begin{figure}[htb!]
	   \center{\includegraphics[width=0.9\textwidth]
	       {./images/DirectoryExcerpts2.png}}
	  \caption{\label{fig:directories} Examples of directory layouts and contents: 1) Duverneuil et La Tynna 1806 - index by name; 2) Deflandre 1828 - index by activity ; 3) Bottin 1851 - index by street name}
\end{figure}

@@

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/protocol.pdf}
    \caption{Data extraction pipeline with two quality control checkpoints. The
    NER Q.A. checkpoint may either assess the NER system lonely (the dashed
    \emph{groundtruth} path) or may evaluate the joint work of a NER
    system with an OCR system.}
    \label{fig.pipeline}
\end{figure}

@@

%1. Entrée/Sortie de l'OCR
\textbf{OCR stage.} The first stage of the pipeline aims at extracting the raw text from the images. 
Individual image fragments are created from each segmented entry and fed to an OCR system for text extraction.
An entry might span over multiple text lines but is
always a single block. Thus, the most adapted mode is chosen when the OCR system allows for the detection mode (e.g. the
\emph{block} mode for \emph{Tesseract}). 
Some glyphs used in this dataset might be unknown to the OCR, and some like
\scalerel*{\includegraphics{./images/LH.png}}{H} do not even have a Unicode codepoint, and were annotated using Unicode Private User Area 1.
Furthermore, as some annotations guidelines where unclear to human annotators, some projections rules were applied: whitespace, dash, dots and a couple of commonly confused characters where projected to well-defined codepoints.
The same normalisation was applied to OCR predictions.
At the end of this first stage, an OCR Quality Assessment (Q.A.) between the \emph{normalised} groundtruth text and the
OCR output is performed on the basis of the $8,765$ entries which were manually controlled, totalling $424,764$ characters (including $54,387$ spacing characters). Entries are $49.0$-characters long on average.

%2. Entrée/Sortie
\textbf{NER Stage.} The second stage of the pipeline aims at extracting the named entities from a text with a NER
system. This text originates from the OCR outputs in a real-word scenario but might be the groundtruth text in order to
evaluate the NER performance independently. There are 5 types of entity to detect~(see.~\cref{tab.entities}).
The NER system has to classify non-overlapping parts of the text into one of these entities (or none of them). A second
Q.A. (namely, NER Q.A.) is performed at the end of this stage between the groundtruth and the NER output.

@@

\begin{table}
\caption{Entities to recognise in the dataset.}
\label{tab.entities}
\small
\begin{tabular}{llp{8cm}}
Entity & Count & Description\\    
PER & 8788 & a person name or a business name, usually referred to as several person names. First names, initials, or civility mentions are included. E.g.: \textit{Alibert (Prosper)}, \textit{Allamand frères et Hersent},\textit{Heurtemotte (Vve)}. \\
TITLE & 483 & an honorary title, either text, glyphs or a combination of the two. E.g: O. \scalerel*{\includegraphics{./images/LH.png}} {H} for \textit{Officier de la Légion d'Honneur} or \scalerel*{\includegraphics{./images/GMLondon.png}}{H} for the Great Medal at the London exhibition.\\
ACT & 6472 & the profession or social status of a person summarised in the single concept of activity. E.g.: \textit{horlogerie}, \textit{export en tous genres}, \textit{Conseiller d'État}, \textit{propriétaire}.\\
LOC & 9709 & mostly street names (\textit{r. de la Jussienne}), but may also be neighbourhoods (\textit{Marais du Temple}) or any indirect spatial references (\textit{au Palais Royal}).\\
CARDINAL & 8747 & a street number, as part of an address (16, 5 bis), or a range of numbers (e.g. 23-25 or 5 \textit{à} 9).\\
FT & 43 & a geographic entity type, used to give more details on a location, e.g. \textit{boutique}, \textit{atelier}, \textit{fab.} or \textit{dépôt}. \\
\end{tabular}
\end{table}

>>>>

\begin{figure}[htb!]
	   \center{\includegraphics[width=0.9\textwidth]
	       {./images/DirectoryExcerpts2.png}}
	  \caption{\label{fig:directories} Examples of directory layouts and contents. \emph{Top}: Duverneuil et La Tynna 1806 - index by name; \emph{Middle}: Deflandre 1828 - index by activity ; \emph{Bottom}: Bottin 1851 - index by street name.}
\end{figure}

@@

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/protocol.pdf}
    \caption{Data extraction pipeline with two quality control checkpoints. The
    NER Q.A. checkpoint may either assess the NER system in isolation (using the dashed
    \emph{groundtruth} path), or may evaluate the joint work of a NER
    system with an OCR system.}
    \label{fig.pipeline}
\end{figure}

@@

%1. Entrée/Sortie de l'OCR
\textbf{OCR stage.} The first stage of the pipeline aims at extracting the raw text from the images. 
Individual image fragments are created from each segmented entry and fed to an OCR system for text extraction.
An entry might span over multiple text lines but is
always a single block. Thus, the most adapted mode is chosen when the OCR system allows for the detection mode (e.g. the
\emph{block} mode for \emph{Tesseract}). 
Some glyphs used in this dataset might be unknown to the OCR, and some like
\scalerel*{\includegraphics{./images/LH.png}}{H}, which do not even have a Unicode codepoint, were annotated using Unicode Private User Area 1.
Furthermore, as some annotations guidelines where unclear to human annotators, some projections rules were applied: whitespace, dash, dots and a couple of commonly confused characters where projected to well-defined codepoints.
The same normalisation was applied to OCR predictions.
At the end of this first stage, an OCR Quality Assessment (Q.A.) between the \emph{normalised} groundtruth text and the
OCR output is performed on the basis of the $8,765$ entries which were manually controlled, totalling $424,764$ characters (including $54,387$ spacing characters). Entries are $49.0$-characters long on average.

%2. Entrée/Sortie
\textbf{NER Stage.} The second stage of the pipeline aims at extracting the named entities from a text with a NER
system. This text can either originate from the OCR outputs in a real-word scenario, or from groundtruth text in order to
evaluate the NER performance independently. There are 5 types of entity to detect~(see.~\cref{tab.entities}).
The NER system has to classify non-overlapping parts of the text into one of these entities (or none of them). A second
Q.A. (namely, NER Q.A.) is performed at the end of this stage between the groundtruth and the NER output.

@@

\begin{table}
\caption{Entities to recognise in the dataset.}
\label{tab.entities}
\small
\begin{tabular}{llp{8cm}}
\toprule
\textbf{Entity} & \textbf{Count} & \textbf{Description}\\    
\midrule
PER & 8788 & a person name or a business name, usually referred to as several person names. First names, initials, or civility mentions are included. E.g.: \textit{Alibert (Prosper)}, \textit{Allamand frères et Hersent},\textit{Heurtemotte (Vve)}. \\
TITLE & 483 & an honorary title, either text, glyphs or a combination of the two. E.g: O. \scalerel*{\includegraphics{./images/LH.png}} {H} for \textit{Officier de la Légion d'Honneur} or \scalerel*{\includegraphics{./images/GMLondon.png}}{H} for the Great Medal at the London exhibition.\\
ACT & 6472 & the profession or social status of a person summarised in the single concept of activity. E.g.: \textit{horlogerie}, \textit{export en tous genres}, \textit{Conseiller d'État}, \textit{propriétaire}.\\
LOC & 9709 & mostly street names (\textit{r. de la Jussienne}), but may also be neighbourhoods (\textit{Marais du Temple}) or any indirect spatial references (\textit{au Palais Royal}).\\
CARDINAL & 8747 & a street number, as part of an address (16, 5 bis), or a range of numbers (e.g. 23-25 or 5 \textit{à} 9).\\
FT & 43 & a geographic entity type, used to give more details on a location, e.g. \textit{boutique}, \textit{atelier}, \textit{fab.} or \textit{dépôt}. \\
\bottomrule
\end{tabular}
\end{table}
